---
title: "GPT_Screening"
author: "Caroline Sutton Chubb"
date: "2023-11-12"
output: html_document
---
Using ChatGPT for Title and Abstract Screening in Systematic Reviews
Source: [https://mikkelvembye.github.io/AIscreenR/articles/Using-ChatGPT-For-Screening.html]

# Preparation
```{r load-pacakges, message=FALSE}
# Installation if missing
install.packages("devtools")
devtools::install_github("MikkelVembye/AIscreenR")

# Load packages 
library(AIscreenR)
library(revtools)
library(tibble)
library(dplyr)
# library(purrr) Removed due to error
library(usethis)
library(future)
library(readr) # To use read_csv
```

```{r prepare-files, warning=FALSE}
# Load RIS file
screen_dat <- revtools::read_bibliography("Screening1_withResults.ris")

# Decision Key
decisions <- read_csv("customizations_log.csv")

# Merge to include decisions

decisions <- decisions %>%
              group_by(article_id, user_id, key)

```

## Create Prompt 
```{r prompt}
prompt <- "Evaluate the following study based on the selection criteria for a systematic review on the use of R statistical programming in the course curriculum for applied research or statistics course at the college and university level. This search will include any studies that examine the use of R in an applied research course at the undergraduate or graduate level. This includes experimental, quasi experimental, observational, and qualitative studies. I would like to assess (1) Did the study include the R programming language? (2) Did the study take place in a college or university setting? (3) Does the study involve discipline(s) other than computer science? (4) Does the look at student experiences?"
```

## Prepare for Test 
Running test with one single study to avoid upcharges. 
```{r subset-test eval=FALSE}
test_data <- subset()
```

## API Key Set Up

```{r eval=FALSE}

```

## Rate Limits
In order to calculate rate limits, you must set up API 
```{r rate-limits, eval=FALSE, include=FALSE}
# Rate limits across one model (Default is "gpt-3.5-turbo-0613")
rate_limits <- rate_limits_per_minute()
rate_limits


# Rate limits overview across multiple models
# Add further models if necessary
models <- c("gpt-3.5-turbo-0613", "gpt-4")

models_rate_limits <- rate_limits_per_minute(model = models) 
models_rate_limits
```
### Price
This price is an estimate of 100% Chat GPT screening.  Price may vary depending on ChatGPT version used. 
```{r API-price}
app_obj <- 
  approximate_price_gpt(
    data = screen_dat, # RIS data
    prompt = prompt, 
    studyid = accession, # indicate the variable with the studyid in the data
    title = title, # indicate the variable with the titles in the data
    abstract = abstract, # indicate the variable with the abstracts in the data
    model = c("gpt-3.5-turbo-0613", "gpt-3.5-turbo-0613", "gpt-4"),
    reps = c(1, 10, 1),
    top_p = c(0.001, 1)
  )

app_obj

app_obj$price_dollar
app_obj$price_data
```
# Screening titles and abstracts
```{r}

```

## Screening failed requests

## Getting the results from the screening

# Analyzing the screening

## Simple table

## False included and excluded (by gpt)
